\textbf{Connor Macdonald}
\begin{itemize}
	\item Rewritten Technical Design Section
	\item Reformatted Functional Requirements and added post-mortem.
\end{itemize}

\textbf{Andrew Clifford}
\begin{itemize}
	\item Reformatted Risks tables
	\item Added discussion subsection to the end of the Risks section
\end{itemize}

\textbf{Taran Jennison}
\begin{itemize}
	\item Minor tweaks in GUI prototypes
	\item Added GUI development and deployment section to discuss how the GUI went from plans to implementation with a short retrospective on how it went
\end{itemize}

\textbf{George Stephenson}
\begin{itemize}
	\item Minor tweaks to design doc in stakeholders and use cases
	\item Added ability to add item tags.
	\item Added ability to change colour of menu items.
	\item Did a lot of converting google docs to latex.
	\item Updated layout of management screen.
\end{itemize}

\noindent\textbf{Anzac Morel}
\begin{itemize}
	\item Implemented acceptance tests that were previously written into the system but not implemented
	\item Implemented a GUI screen that allowed the user to set an initial cash float
	\item Moved the add stock button to the stock tab of the management screen - Had to implement a new GUI screen where the user can select the item they want to add stock for
	\item Moved the add to menu button to the menu tab of the management screen - Had to implement a new GUI screen where the user can select the item they want to add
	\item Rewrote the acceptance testing section of the design document into Latex
	\item Rewrote the project timeline section of the design document into Latex
\end{itemize}

\textbf{Hamesh Ravji}
\begin{itemize}
	\item Rewritten Executive Summary
	\item Rewritten System Context and Relevant Business Information
	\item Rewritten Deployment Model
	\item Rewritten Data Modelling
	\item Written Project Description
\end{itemize}

\textbf{Rchi Lugtu}
\begin{itemize}
	\item Rewritten quality requirements, and before there were too many quality requirements, so now I have made it clear and concised, and kept the important quality requirements for this project.
	\item Added a key drivers to the table, and a section that explains the result from the key drivers table.
	\item Added the quality testing, and added the testing procedures, and had 3 subsections for it explaining the functional testing, quality testing, and overall discussion.
	\item Added the refund order functionality in the management screen
\end{itemize}