\textbf{Deliverable 1:\\}
The first week of the deliverable was spent getting to know members of the team, establishing a team policy and setting up tools that would be used throughout the project (design document, trello board etc). After this initial phase had been completed, a meeting was held to create and distribute tasks. This was done by creating a trello card for each task that needed to be completed. Then each group member assigned them selves to a card or cards and they were to complete the associated task before the next meeting. This same method was used for the entire first deliverable and with continual updating of tasks each week meant that the team was able to complete all tasks required without a large push close to the deadline. One issue with this method is that with team meetings being used primarily for task distribution all tasks were completed by individuals. The problem with this is that most if not all of the tasks required collaboration and therefore the quality of our deliverable suffered as a result.\\
\\
\textbf{Deliverable 2:\\}
No work was completed during the first week of the deliverable as other commitments were priority at this time. After this a meeting was had to discuss the second deliverable and again create and allocate tasks. This was heading into the mid semester breaks which meant that meeting up and communicating as a whole group was going to be more difficult as some people would not be in Christchurch during the break. To combat this those still in Christchurch had meetings as per usual while a summary was created and send to the other members of the group and they were advised to check trello and assign themselves tasks. No main functionality of the system was implemented over the break only base classes. Once break was over it was time to tackle some of the larger classes and main functionality of the system. After a week it was found that our current system for completing tasks was not going to work any more as the tasks were larger and a lot more communication was required. Therefore we adapted by adding more meetings where we would all come together to work on the project. These peer programming sessions proved to be successful as we again were able to complete all the tasks required without a large push close to the deadline. One thing that we learnt from this deliverable is that even though the project code was well underway the design document should not be left behind. During the second deliverable the design document was just an after though and this wasn't good enough as it should be an active document that accurately reflects our system and we would have to make up for this in during the third deliverable.\\
\\
\textbf{Deliverable 3:\\}
No work was completed during the first week as other commitments were priority at this time. After thus a meeting was held to discuss what tasks to prioritize. This was important as we needed to make sure that it was clear what tasks were going to maximise our number of marks while being achievable in the time remaining. The tasks that were decided upon were made into trello cards and were to be completed within the week. During the third week the final trello cards completed and final tweaks and bug fixes on the project completed. Overhaul of the design document begun, moving from google docs to latex as well as updating each section from the design document. This was thought to be necessary as our design document was severely lacking in quality and google docs was not stable enough to allow all members of our team to work on it at the same time. A lot of effort was put in during the final week which was to be expected. During week two, although we were able to complete a lot of work towards the project it was not enough. We did not follow the deadline we set for ourselves strictly enough and this caused us to have to put in a lot more effort in the final week then we had initially planned.  \\
\\
\textbf{Overall:\\}
Overall the team worked well together and we were able to complete the project to a good standard. Looking back there is a lot to be improved on in terms of planning. One things that was discussed in the lab times is getting the most out of the tools we are using. It was not until the third deliverable that we were adding anything more than just a name to a trello card. Adding deadlines and check boxes in earlier deliverables would have been beneficial as it would have helped to get tasks done correctly the first time and to help solidify the deadlines that we set for ourselves. Also taking an entire week off was not a good idea especially considering that we did it multiple times. This time should have been used to at least plan ahead and complete smaller tasks. Finally, the peer programming sessions that we implemented during the second deliverable should have been something that we did from the very start as they increased the quality of our work as well as keeping everyone on the same page.\\
\\
